Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-06 Manuscript/manuscript.Rmd
updates
Where? Don't see it on Figure 5, which exists in two versions (?); !!!figure5_v2_allnoneperfs, will delete other figures after meeting if deemed appropriate

We first assessed performances on random forest models built on fully unbalanced training sets across each resolution, for each predictor type (Figure 5) [??? Why not distance?; !!!included a  more desciptive plot with distance ??? Where? Don't see it on Figure 5, which exists in two versions (?)]. When looking at the the conventional metrics used for assessment (accuracy and AUC), models that were not corrected for class imbalance appeared to perform reasonably well.  However, when we considered the F1-score and MCC, we observed a significant degradation in performance across both resolution and predictor type. This was due in part to each models' inability to correctly classify the genomic bins that overlapped with flanked TAD boundaries (true positives, Supplementary Table 3). Even without correcting for the class imbalance, we found that, within predictor types, models with distance type predictors consistently outperformed the other two predictor types across all performance metrics.

@@

>>>>

We first assessed performances on random forest models built on fully unbalanced training sets across each resolution, for each predictor type (Figure 5) [??? Why not distance?; !!!included a  more desciptive plot with distance ??? Where? Don't see it on Figure 5, which exists in two versions (?); !!!figure5_v2_allnoneperfs, will delete other figures after meeting if deemed appropriate]. When looking at the the conventional metrics used for assessment (accuracy and AUC), models that were not corrected for class imbalance appeared to perform reasonably well.  However, when we considered the F1-score and MCC, we observed a significant degradation in performance across both resolution and predictor type. This was due in part to each models' inability to correctly classify the genomic bins that overlapped with flanked TAD boundaries (true positives, Supplementary Table 3). Even without correcting for the class imbalance, we found that, within predictor types, models with distance type predictors consistently outperformed the other two predictor types across all performance metrics.

@@

## Table 3: Model Performances When Not Accounting for Class Imbalance

A list of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.
